Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Edit stellar mass measurement 1

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis.
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            It is a very conservative estimate of the region that we can not reliable 
            extract 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
    $2.0^{\arcsec}$ matching radius. 
    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
    included in our sample. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of our redshifts comes from the BOSS and SDSS ``legacy'' LRG samples. 
    The GAMA survey provides an additional $14$\% of spec-$z$.
    Although the GAMA survey only covers parts of the \texttt{S15B} data release, 
    hence affects the homogeneity of our sample, it will not affect the results of 
    this work.
    We will discuss this more in \S \ref{sec:final}.

    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Redshift evolution in the stellar population properties can be largely 
    ignored.  
    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. 
    And finally, the over-subtraction of the background level becomes a more serious 
    issue at lower redshifts.  
    We will now describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
    and our stellar mass estimates (\S \ref{sec:mstar}). 
    We will then define the final sample in \S \ref{sec:final}.

@@

    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
    in radius, along with a bad pixel mask and the PSF model. 
    These postage-stamps include all of the light of the galaxy and are large enough 
    to also evaluate the background level. We choose to use $i$-band images because 
    they trace the stellar mass distributions of massive galaxies at 
    $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

@@

@@

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    Although \cmodel{} tends to underestimate the total flux for bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipe}).

>>>>

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
            \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis.
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            It is a very conservative estimate of the region that we can not reliable 
            extract 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the mean ellipticity used for the 
            final isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
    $2.0^{\arcsec}$ matching radius. 
    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
    included in our sample. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our goal.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of our redshifts comes from the BOSS and SDSS ``legacy'' LRG samples. 
    The GAMA survey provides an additional $14$\% of all spectroscopic redshifts.
    Although the GAMA survey only covers parts of the \texttt{S15B} data release, 
    hence affects the homogeneity of our sample, it will not affect the results of 
    this work.
    We will discuss this more in \S \ref{sec:final}.

    We choose the redshift range $0.3 \leq z \leq 0.5$ to make sure that: 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues so that the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Redshift evolution in the stellar population properties can be largely 
    ignored.  
    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. 
    And finally, the over-subtraction of the background level becomes a more serious 
    issue at lower redshifts.

    We will now describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
    and our stellar mass estimates (\S \ref{sec:mstar}). 
    We will then define the final sample in \S \ref{sec:final}.

@@

    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
    in radius, along with a bad pixel mask and the PSF model. 
    These postage-stamps include all of the light of the galaxy and are also large 
    enough to also evaluate the background level. We choose to use $i$-band images 
    because they trace the stellar mass distributions of massive galaxies at 
    $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

@@

    We should point out that both \minn{} and \mtot{} are measured within the same 
    elliptical aperture. 
    The 10 kpc and 100 kpc here refer to the radius along the major aixs of the 
    elliptical isophote.

@@

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipe}).
